Weak interspecific interactions in a sagebrush steppe: evidence from observations, models, and experiments

### 2018-04-07 removals/Manuscript/appendix.tex
Finalized appendix

\subsection{Correcting for Jensen's inequality in one-step-ahead projections} 
One-year-ahead projections of cover in each quadrat, based on its state in the current year, were made using the regression models for survival and growth. 
For each genet present in year $t$, we computed its probability of survival and its expected total cover in year $t+1$, incorporating the random 
year-effects for year $t$ and quadrat group effects. The projected cover in year $t+1$ is the sum over all plants in year $t$ of survival probability times  
projected mean size in year $t+1$ conditional on survival.

>>>>

\subsection{Correcting for Jensen's inequality in one-step-ahead projections} 
One-year-ahead projections of cover in each quadrat, based on its state in the current year, were made using the regression models for survival, growth and recruitment. 
For each genet present in year $t$, we computed its probability of survival and its expected total cover in year $t+1$, incorporating the random 
year-effects for year $t$ and quadrat group effects. The projected cover in year $t+1$ is the sum over all plants in year $t$ of survival probability times  
projected mean size in year $t+1$ conditional on survival, plus the number of expected recruits multiplied by mean recruit size.
